\section{Update of the MySQL Database}\label{task4}

In kitting, the robot moves parts and kit trays in the workstation from an initial state to a goal state in order to build a kit. To guarantee that state relations use current information of objects in the environment (kit trays, parts, etc), it is necessary to update the MySQL database once the locations and orientations of these objects change in the environment. Therefore, the kitting domain needs to include an approach that updates the MySQL database when the configuration of the workstation changes, namely, after a PDDL action has been performed by the robot.

\subsection{Proposed Research}
We propose to develop a methodology that updates the MySQL database when the locations of objects in the workstation are modified by the execution of an action. The new methodology will identify objects of interest involved in the execution of an action by analyzing the parameters of this action in the PDDL plan file. Once an action is executed by the robot, the location of some of these objects (parameters) will be updated in the MySQL database. \\We consider the PDDL action (\texttt{take-kittray} \const{robot\_1} \const{kit\_tray\_1} \const{empty\_kit\_tray\_supply} \const{tray\_gripper} \const{work\_table\_1}) that is intended to pick up a kit tray (\const{kit\_tray\_1}) from a box of empty kit trays (\const{empty\_kit\_tray\_supply}). In this action, \const{kit\_tray\_1} is the object of interest which location will vary during the execution of this action. The proposed methodology will be able to identify \const{kit\_tray\_1} as the object of interest for the action \texttt{take-kittray} and will thus update the location of \const{kit\_tray\_1} in the MySQL database once this action is performed. 