%% This file  is based off of `elsarticle-template-1a-num.tex',
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
%\usepackage{amsfonts}
\usepackage{color}
\usepackage{amsmath}%%% -- Added by Zeid to use \begin{gather}...\end{gather}
\usepackage{rotating}%%% -- Added by Zeid for tabular
\usepackage{multirow}%%% -- Added by Zeid for tabular
%% The amsthm package provides extended theorem environments
 \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}


\newcommand{\class}[1] {\textsf{#1}}
\newcommand{\onto}[1] {\textsl{#1}}
\newcommand{\process}[1] {\textmd{#1}}
\newcommand{\stvar}[1] {\textsf{#1}}
\journal{Robotics and Automation}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Knowledge Driven Robotics}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[NIST]{Stephen Balakirsky}
\author[NIST,UMD]{Zeid Kootbally}
\author[CATHU,NIST]{Thomas Kramer}
\author[NIST]{Anthony Pietromartire}
\author[NIST]{Craig Schlenoff}

\address[CATHU]{Catholic University of America, Washington, DC, USA}
\address[NIST]{National Institute of Standards and Technology, Gaithersburg, MD USA}
\address[UMD]{University of Maryland, College Park, MD, USA}

\begin{abstract}
%% Text of abstract
In this article,  a newly developed knowledge architecture that was designed to support the IEEE Robotics and Automation Society's Ontologies for Robotics and Automation Working Group
will be presented. This architecture allows for the creation of systems that demonstrate flexibility, agility, and the ability to be rapidly re-tasked. The architecture, as well as
an implementation that combines extensions to the Unified System for Automation and Robot Simulation (USARSim) and the Robot Operating System (ROS), will be discussed
in detail. This implementation extends USARSim and ROS to provide models of industrial robots and end-effectors while providing a case study in the area of robotic kit building.
The architecture's potential for creating flexible, agile, and rapidly re-taskable systems will be presented, and possible areas of future work will be discussed.
\end{abstract}

\begin{keyword}
Don't forget to add keywords
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text
\section{Introduction}
\label{sect:introduction}
Today's state-of-the-art industrial robots are capable of sub-millimeter accuracy \cite{RobotAccuracy}.
However, they are often programmed by an operator using crude positional controls from a teach pendent. 
Reprogramming these robots when their task is altered requires that the robot cell be taken off-line for a
human-led teaching period.  For small batch processors or other customers who must frequently change
their line configuration, this frequent down time may be unacceptable. 
The robotic systems of tomorrow
need to be capable, flexible, and agile.  These systems need to perform their duties at least 
as well as human counterparts, be able to be quickly re-tasked to other operations,
and be able to cope with a wide variety of unexpected environmental and operational changes. 
In order to be successful, these systems need to combine domain expertise,
knowledge of their own skills and limitations, and both semantic and geometric environmental information.

The IEEE Robotics and Automation Society's Ontologies for Robotics and Automation Working group is 
striving to create an overall ontology and
associated methodology for knowledge representation and reasoning that will address these 
knowledge needs. As part of the
Industrial Subgroup of the IEEE Working Group, the authors have been examining a novel 
architecture that allows for the combination of the static
aspects of the ontology with dynamic sensor processing to allow for a robotic system that 
is able to cope with environmental and task changes
without operator intervention.

This article presents a formal knowledge model and implementation methodology
that has been developed by the industrial subgroup
of the IEEE Working Group. The knowledge model allows for the compact representation
of the world knowledge required to successfully plan for and carry out industrial applications.
The methodology presents sample techniques that demonstrate how this knowledge can by transformed
into representations that are optimized for 
The knowledge methodology/model proposed in this article is not designed to act as a stand-alone
system architecture. Rather it is intended to be an extension to well developed hierarchical, 
deliberative architectures such as 4D/RCS \cite{Albus2000}. The methodology relies on the robotic system
to be able to formulate high-level, goal oriented plans and to be able to carry out
specific robot motions. The knowledge model i

In order to become accepted in industrial applications, tomorrow\rq{}s systems will need to do more. 
They will have to demonstrate flexibility through the
elimination of hand-tuned parameters. They will need to demonstrate agility through the 
ability to cope with rapidly changing situations and task requirements,
and they will need to be able to be rapidly re-tasked in order to adapt 
to new tasking quickly and efficiently. The  industrial subgroup of the
Ontologies for Robotics and Automation Working group is striving to demonstrate 
that the inclusion of knowledge in the form of an ontology
will allow robotic systems to progress to this next level.

The organization of the remainder of this paper is as follows: Section \ref{Sect:Methodology} presents an overview of the knowledge driven methodology that
has been developed for this effort. Section \ref{Sect:Kitting} describes the domain of kit building
which is a greatly simplified, but still practically useful manufacturing/assembly domain. Section \ref{Sect:Ontology} describes our ontology for the kitting
domain. Section \ref{Sect:Implementation} describes the implementation of the system and Section \ref{Sect:Conclusion} provides for conclusions and
future work.


\section{Design Methodology}
\label{Sect:Methodology}
\input{Architecture}

\section{Industrial Kitting}
\label{Sect:Kitting}
\input{kitting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ontology}
\label{Sect:Ontology}
\input{Ontology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
\label{Sect:Implementation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{Sect:Conclusion}
\input{conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1a-num-names}
\bibliography{elsevier}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1a-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}


\end{document}

%%
%% End of file `elsarticle-template-1a-num.tex'.
