% LaTex file for Stephen Balakirsky's RITA 2014 submission
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
%
% my additional packages
\usepackage{graphicx}
\usepackage{multirow,array}
\usepackage{rotating} % for sideways
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{algorithm2e}
\usepackage[linesnumbered, boxed, figure]{algorithm2e}
%
% zeid's definitions
\newcommand{\class}[1] {\textit{#1}}
\newcommand{\const}[1] {$\mathit{#1}$}
\newcommand{\objvar}[1] {$\mathsf{#1}$}
\newcommand{\stvar}[1] {\textsf{#1}}
%
%
\begin{document}
%
\frontmatter          % for the preliminaries
%
\pagestyle{headings}  % switches on printing of running heads
\addtocmark{Hamiltonian Mechanics} % additional mark in the TOC
%
%
\mainmatter              % start of the contributions
%
\title{An Ontology Based Approach to Action Verification for Agile Manufacturing}
%
\titlerunning{Agile Manufacturing}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Stephen Balakirsky\inst{1} \and Zeid Kootbally\inst{2}}
%
\authorrunning{Stephen Balakirsky et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Stephen Balakirsky, Zeid Kootbally}
%
\institute{Georgia Tech Research Institute, Atlanta, GA 30332, USA,\\
\email{stephen.balakirsky@gtri.gatech.edu},\\ WWW home page:
\texttt{unmannedsystems.gtri.gatech.edu}
\and
University of Maryland, College Park, MD 20740, USA,\\
\email{zeid.kootbally@umd.edu},\\ WWW home page:
\texttt{www.nist.gov/el/isd/ks/kootbally.cfm}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
Many of today's robotic work cells are unable to detect when an action failure has occurred. This results in faulty products being sent down the line, and/or downtime for the cell as failures are detected and corrected. This article examines a novel knowledge-driven system that provides added agility by detecting and correcting action failures. The system also provides for late binding of action parameters, thus providing flexibility by allowing plans to adapt to changing environmental conditions. The key feature of this system is its knowledge base that contains the necessary relationships and representations to allow for failure detection and correction. This article presents the ontology that stores this knowledge as well as the overall system architecture. The manufacturing domain of kit construction is examined as a sample test environment. 
\keywords{failure detection, manufacturing, ontology, robotics, PDDL}
\end{abstract}
%
%
\input{introduction}
\input{systemOverview}
\input{systemOperation}
\input{failureAnalysis}
\input{conclusions}
%
%



%
% ---- Bibliography ----
%
\bibliographystyle{plain}
\bibliography{rita2013}
\clearpage
\addtocmark[2]{Author Index} % additional numbered TOC entry
\renewcommand{\indexname}{Author Index}
\printindex
\clearpage
\addtocmark[2]{Subject Index} % additional numbered TOC entry
\markboth{Subject Index}{Subject Index}
\renewcommand{\indexname}{Subject Index}
%\input{subjidx.ind}
\end{document}
