% LaTex file for Stephen Balakirsky's Robotics and 
% Computer Integrated Manufacturing 2014 submission
%
\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}

%
% my additional packages
\usepackage{graphicx}
\usepackage{multirow,array}
\usepackage{rotating} % for sideways
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{algorithm2e}
\usepackage[linesnumbered, boxed, figure]{algorithm2e}
%
% zeid's definitions
\newcommand{\class}[1] {\textit{#1}}
\newcommand{\const}[1] {$\mathit{#1}$}
\newcommand{\objvar}[1] {$\mathsf{#1}$}
\newcommand{\stvar}[1] {\textsf{#1}}
%
%
%
\modulolinenumbers[5]

\journal{Journal of Robotics-and-Computer-Integrated-Manufacturing}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Ontology Based Action Planning and Verification for Agile Manufacturing}

%% Group authors per affiliation:
\author{Stephen Balakirsky}
\address{Georgia Tech Research Institute, Atlanta, GA 30332, USA}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{stephen.balakirsky@gtri.gatech.edu}

\begin{abstract}
Many of today's robotic work cells are unable to adapt to even small changes in tasking without significant reprogramming. 
This results in downtime for production
lines anytime a change to a product or procedure must be made. This article examines a novel 
knowledge-driven system that 
provides added agility by removing the programming burden for new activities from the robot 
and placing it in the knowledge representation. The system is able to automatically 
recognize and adapt to changes in its work-flow and dynamically change assignment details. 
The system also provides for 
action verification and
late binding of action parameters, 
thus providing flexibility by allowing plans 
to adapt to production errors and changing environmental conditions. The key feature of this system is its knowledge base that 
contains the necessary 
relationships and representations to allow for
adaptation. This article presents the ontology that stores this knowledge as well as the 
overall system architecture. 
The manufacturing domain of kit construction is examined as a sample test environment. 
\end{abstract}

\begin{keyword}
\texttt{knowledge driven system, adaptive planning, manufacturing, ontology, robotics, Planning Domain Definition Language}
\end{keyword}

\end{frontmatter}

\linenumbers

%
%\usepackage{makeidx}  % allows for indexgeneration
%
%
%
\input{introduction}
\input{pddl}
\input{systemOperation}
\input{knowledgeRepresentation}
\input{conclusions}
%
%



%
% ---- Bibliography ----
%
%\bibliographystyle{plain}
\bibliography{ontology}
\end{document}
