Applications for assembly robots have been primarily implemented in fixed and programmable automation. Fixed automation is a process using mechanized machinery to perform fixed and repetitive operations in order to produce a high volume of similar parts. In programmable automation, products are made in batch quantities ranging from several dozen to several thousand units at a time. 
Although today's state-of-the-art industrial robots are capable of sub-millimeter accuracy~\cite{RobotAccuracy}, they are often programmed by an operator using crude positional controls from a teach pendant. Moreover, drastic modifications in the design process are realized when parts need major changes or become to complicated in design, thus resulting in long set up time to accommodate the new product style.

Reprogramming these robots when the aforementioned conditions arise requires that the robot cell be taken off-line for a human-led teaching period. For small batch processors or other customers who must frequently change their line configuration, this frequent down time may be unacceptable. The robotic systems of tomorrow need to be capable, flexible, and agile. These systems need to perform their duties at least as well as human counterparts, be able to be quickly re-tasked to other operations, and be able to cope with a wide variety of unexpected environmental and operational changes. In order to be successful, these systems need to combine domain expertise, knowledge of their own skills and limitations, and both semantic and geometric environmental information. The challenge of expanding industrial use of robots is through flexible automation where minimized setup times can lead in to more output and generally better throughput. Flexible robots are required to be quickly reconfigured for design and process modifications. Furthermore, they need to be information driven so that they can reliably perform different sequences of actions on command. The cost for generating the information that drives the actions must be kept down and the information must be accurate.

This paper discusses a flexible kitting system. Kitting is the process in which several different, but related items are placed into a container and supplied together as a single unit (kit). Kitting itself may be viewed as a specialization of the general bin-picking problem. In industrial assembly of manufactured products, kitting is often performed prior to final assembly. Kitting, when applied properly, has been observed to show numerous benefits for the assembly line, such as cost savings \cite{Carlsson_2008} including saving manufacturing or assembly space \cite{Medbo2003}, reducing assembly workers walking and searching times \cite{Schwind1992}, and increasing line flexibility \cite{Bozer1992} and balance \cite{Jiao2000}. In industrial assembly of manufactured products, kitting is often performed prior to final assembly. 

The increasing global competition demands the manufacturing industry to move towards state-of-the-art flexible systems. Therefore, it is important not only to know how to measure the complexity of an assembly operations -- the tasks that consist a plan -- but also to evaluate how well these operations are carried out by a manufacturing process. Recently, some theoretical measures have been explored to evaluate an assembly sequences under different contexts. For example, Sanderson and Homem de Mello~\cite{SANDERSON.1987} used the And/Or graph approach to represent feasible assembly/disassembly sequences and a function based on parts entropy measures as evaluation criteria for search in the And/Or graph space. Park \textit{et al.}~\cite{PARK.1991} described the evaluation criteria based on four evaluation functions to minimize the chances of assembly failures caused by spatial errors of parts and assembly equipment. Bonneville \textit{et al.}~\cite{BONNEVILLE.1995} presented a genetic algorithm that uses the assembly trees as model for the plans to encode them in chromosomes. The liaisons graph and the geometric constraints of the model are then used to evaluate the assembly operations. Su\'{a}rez and Lee~\cite{SUAREZ.1997} proposed a statistical measure of an assembly cost index to evaluate the assembly sequences in order to determine the optimal one.


This paper presents a system that evaluates the performance of kitting applications through simulation using specific metrics. The authors have developed a canonical robot control language (CRCL)~\cite{NISTIR.Balakirsky} that attempts to be a lowest common denominator of robot programing languages. It is anticipated that kitting plans can be translated into CRCL command sets which may then be evaluated by standardized metric software. The CRCL command sets may then be translated into a specific robot platform's language.

The organization of the remainder of this paper is as follows: Section~\ref{sect:knowledge_driven_methodology} presents an overview of the knowledge driven methodology that has been developed for this effort. Section~\ref{sect:KittingViewer} describes the Kitting Viewer tool that
simulates the execution of a plan (CRCL command file) for changing a kitting workstation from an initial state to a goal state. Section~\ref{sect:Metrics} reviews the test method and metrics that are used to compare the performance of different kitting planning systems. Section~\ref{sect:Scoring} describes a configurable scoring system that uses the five factors combined as specified by a scoring file to compute
the score of the plan and Section~\ref{sect:Conclusions} concludes this paper and discusses future work.


